\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,graphicx,enumerate}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\def\Homework{7} % Number of Homework
\def\Session{Spring 2019}
\def\Section{B}
\def\MyEmail{guybymatlab@gmail.com}
\def\DateOfSubmission{ --------- }

\title{MATLAB Assignment \Homework}
\author{\Session, Section \Section}
\date{}

\newenvironment{qparts}{\begin{enumerate}[{(}a{)}]}{\end{enumerate}}

\textheight=9in
\textwidth=6.5in
\topmargin=-.75in
\oddsidemargin=0.25in
\evensidemargin=0.25in

\begin{document}
\maketitle
In this assignment, you will reinforce what we did in lecture today
regarding MATLAB's filter toolbox.
This assignment is due in two weeks.
Please submit this homework as a \textit{.m} file, 
with suppressed output.
Remember that all lectures and homeworks may be found at 
\textit{github.com/guybaryosef/ECE210-materials}.
Homework is due on \DateOfSubmission to \MyEmail.

For each of the following questions,
generate filters using either \emph{fdatool} or the filter design toolbox in
the signal processing toolbox.
Apply the filter to the signal using \emph{filter}.
Lastly, plot the Fourier Transform of the final result using \emph{fft} and \emph{plot}.
Refer to the notes for the proper way to use \emph{fft} and obtain the proper scaling.

1. Generate a signal that consists of a sum of sine waves of frequencies 1 to 50 kHz.
Set t to be from 0 to 2 seconds, using an interval of 0.001s. 

$$ signal = \sum_{f=1}^{50000} sin(2\pi ft)$$

2. Create a Butterworth lowpass filter with a sampling frequency of Fs = 100 kHz,
a passband frequency of Fpass = 10 kHz, a stopband frequency of Fstop = 20 kHz,
a passband attenuation of Apass = 5dB, and a stopband attenuation of Astop = 50dB.

3. Create a Chebychev I highpass filter with a sampling frequency of Fs = 100 kHz,
a passband frequency of Fpass = 35 kHz, a stopband frequency of Fstop = 15 kHz,
a passband attenuation of Apass = 2dB, and a stopband attenuation of Astop = 40dB.

4. Create a Chebychev II bandstop filter with a sampling frequency of Fs = 100 kHz,
a passband frequency of below the frequency Fpass1 = 5 kHz and above Fpass2 = 45 kHz,
a stopband frequency of between Fstop1 = 15 kHz Fstop2 = 35kHz,
a passband attenuation of Apass = 5dB, and a stopband attenuation of Astop = 50dB.

4. Create a Elliptic bandpass filter with a sampling frequency of Fs = 100 kHz,
a stopband frequency of below the frequency Fstop1 = 15 kHz and above Fstop2 = 35 kHz,
a passband frequency of between Fpass1 = 20 kHz Fpass2 = 30 kHz,
a passband attenuation of Apass = 5dB, and a stopband attenuation of Astop = 50dB.

\end{document}