\documentclass[12pt]{article}
\setlength\parindent{0pt}

\usepackage{geometry}
\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    top=20mm,
 }

\begin{document}

\pagenumbering{gobble}

\title{ECE-210-A Syllabus}
\date{}
\author{Instructor: Guy Bar Yosef}
\maketitle

\textbf{Meeting Time:} Wednesday, 4:00PM - 4:50PM \\
\textbf{Room:} 806 \\
\textbf{Email:} guybymatlab@gmail.com \\

\textbf{Course Overview:}
The course material for ECE-210 is a survey of 
MATLAB as a programming language, specifically tailored but not 
limited to its applications in the realm of signal processing. 
Signals and Systems is a corequisite in the sense that the material 
from ECE-210 is necessary to perform well in that course, but no substantial 
knowledge from Signals and Systems is expected of students in ECE-210. \\
 
This course is 0 credits and your final grade will be either Pass or Fail.
Homeworks need to be submitted both electronicallly AND as a hard copy.
Unless otherwise stated, they will be due the following class 
(ie by 4 pm the next day we have class).
You should submit the homework electornically to guybymatlab@gmail.com as 
\textit{.m} files and also bring a hardcopy of the code in to class. 
\\

\textbf{Grading Policy:}
There will be 9 homeworks assigned. 
You must accumulate a total of 12 points to pass this class.
Each homework assignment will award you 0, 1, or 2 points
(i.e. you do not need to do all of them).
\begin{description}
    \item [$\bullet$]A 0 is assigned if the homework is not handed 
    in at all or if it is wholly incorrect.
    \item [$\bullet$]A 1 is assigned if the homework is handed
    in with many incorrect answers, bad style, or if it is late.
    \item [$\bullet$]A 2 is assigned if the homework runs correctly
    (for the most part), has good style, and is handed in on time.
\end{description} 
If a homework was turned in on time and received a 1,
it may be resubmitted within one week to be regraded.
Unless given permission, no homework will be accepted more than one 
week past its due date. 
Homework assignments will be graded and returned within two weeks.
Some homeworks may include bonus points, but this is not guaranteed.
\\

Attendance is mandatory, and an unexcused absence means that you may
receive no more then 1 point for your next homework assignment. 
If you must be absent for any reason, please email me before lecture begins. \\
% Attendance may be paid to either other section of ECE-210, however both 
% myself and the instructor of the other section must be made aware if you 
% wish to attend a section you are not registered for. 
% Homeworks are different between sections, however, and students registered 
% for ECE-210-A must submit the homework for ECE-210-A.\\

\textbf{Contact:}
Any questions regarding the homeworks or lecture may be emailed 
to me at any time.
MATLAB inquiries may be made to Samuel Maltz and Aziza Almanakly, 
the instructors of the other two sections of ECE-210, as well. 
% Face-to-face tutoring may be offered through the Electrical 
% Engineering department, appointments for which can be made by emailing me. 
Questions regarding Signals and Systems may be directed towards myself, 
although they are often better left for Professor Fontaine. 
If I do not respond to an email in apt time, 
chances are that I am not ignoring you. 
Please just email me again!
All course materials, including homeworks and lessons,
can be found on my Github \textit{github.com/guybaryosef/ECE210-materials}.

\end{document}
